---
title: "plot2"
author: "AM"
date: "2026-02-04"
output: html_document
---

fips: A five-digit number (represented as a string) indicating the U.S. county

SCC: The name of the source as indicated by a digit string (see source code classification table)

Pollutant: A string indicating the pollutant

Emissions: Amount of PM2.5 emitted, in tons

type: The type of source (point, non-point, on-road, or non-road)

year: The year of emissions recorded

```{r}
library(dplyr)
library(ggplot2)
library(RColorBrewer)

#Read in the actual data
nei <- readRDS("summarySCC_PM25.rds")

#Make all the names lower case since I think it's annoying
names(nei) <- tolower(names(nei))

#Read in table to link SCC strings to source names
scc <- readRDS("Source_Classification_Code.rds")
```

Have total emissions from PM2.5 decreased in the Baltimore City, Maryland (
fips == "24510" from 1999 to 2008? Use the base plotting system to make a plot answering this question.

```{r}
#Step 1 - Subset out only fips 24510

baltimore <- subset(nei, fips == "24510")

#I can do the exact same code as before

#------------Step 1: Separate out by year and take means (tapply) ------------#
emimeans <- tapply(baltimore$emissions, baltimore$year, mean, na.rm = TRUE) #Oh whoa. This worked

#Double check output with dplyr
baltimore %>% group_by(year) %>% summarize(meanemissions = mean(emissions, na.rm = TRUE))

#---------------------------Step 2: Plot the points ---------------------------#

#Maybe a barplot would be better than a scatterplot since it's one value / year
barplot(height = emimeans, #mean emission value stored in this vector
        names.arg = as.character(unique(baltimore$year)),
        col = brewer.pal(4, "Set3"),
        xlab = "Year",
        ylab = "Emissions (tons)",
        ylim = c(0, 8))

```

