---
title: "plot5"
author: "AM"
date: "2026-02-04"
output: html_document
---

fips: A five-digit number (represented as a string) indicating the U.S. county

SCC: The name of the source as indicated by a digit string (see source code classification table)

Pollutant: A string indicating the pollutant

Emissions: Amount of PM2.5 emitted, in tons

type: The type of source (point, non-point, on-road, or non-road)

year: The year of emissions recorded

```{r}
library(dplyr)
library(ggplot2)
library(RColorBrewer)

#Read in the actual data
nei <- readRDS("summarySCC_PM25.rds")

#Make all the names lower case since I think it's annoying
names(nei) <- tolower(names(nei))

#Read in table to link SCC strings to source names
scc <- readRDS("Source_Classification_Code.rds")
```

How have emissions from motor vehicle sources changed from 1999–2008 in Baltimore City?

```{r}
#Let's subset nei again

baltimore <- nei %>% filter(fips == "24510")
```

Mobile - On-Road Gasoline Light Duty Vehicles      
Mobile - On-Road Gasoline Heavy Duty Vehicles     
Mobile - On-Road Diesel Light Duty Vehicles        
Mobile - On-Road Diesel Heavy Duty Vehicles  

These are rows 21-24 in scc$EI.Sector

```{r}

vehicle <- unique(scc$EI.Sector)[21:24] #Get only the 21-24 rows

sccvehicle <- scc %>% filter(EI.Sector %in% vehicle) #Get only the scc rows for vehicles

#Subset the baltimore data to just have the vehicle data
bmorevehicle <- baltimore %>% filter(scc %in% sccvehicle$SCC)

#I now have a data frame with just the rows for vehicle emissions
#Just need to plot the emissions now

bmorevehicle$year <- factor(bmorevehicle$year)

ggplot(data = bmorevehicle, aes(x = year, y = emissions)) +
  stat_summary(fun = mean, geom = "bar", aes(fill = year)) +
  xlab("Year") +
  ylab("Vehicle Emissions (tons)") +
  labs(title = "Vehicle Emissions (tons) by Year") +
  theme_minimal() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

