---
title: "plot4"
author: "AM"
date: "2026-02-04"
output: html_document
---
fips: A five-digit number (represented as a string) indicating the U.S. county

SCC: The name of the source as indicated by a digit string (see source code classification table)

Pollutant: A string indicating the pollutant

Emissions: Amount of PM2.5 emitted, in tons

type: The type of source (point, non-point, on-road, or non-road)

year: The year of emissions recorded

```{r}
library(dplyr)
library(ggplot2)
library(RColorBrewer)

#Read in the actual data
nei <- readRDS("summarySCC_PM25.rds")

#Make all the names lower case since I think it's annoying
names(nei) <- tolower(names(nei))

#Read in table to link SCC strings to source names
scc <- readRDS("Source_Classification_Code.rds")
```

Across the United States, how have emissions from coal combustion-related sources changed from 1999–2008?
```{r}
#Which code corresponds to coal combustion-related sources

#Let's just find every row that mentions coal

#Tell apply to loop over scc, and to go by row and look at each column
#use any() to collapse down the result from grepl() so that if any column is TRUE
#The row receives a value of TRUE and can be kept after subsetting

res <- apply(scc, 1, function(x) any(grepl("[Cc]oal",x))) 

coal <- scc[res, ]

#the coal data frame just has every row that contains the word "Coal" or "coal"
#It looks like EI.Sector might give me what I'm looking for

#Let me just do grepl() on EI.Sector and see what is coal-related
unique(scc[grepl("[Cc]oal", scc$EI.Sector), ]$EI.Sector)
```

After doing some exploration with grepl(), it looks like the variable I need to use is EI.Sector - this should tell me anything that's related to coal combustion. There are three variables:

Fuel Comb - Electric Generation - Coal      
Fuel Comb - Industrial Boilers, ICEs - Coal
Fuel Comb - Comm/Institutional - Coal   

```{r}

#Create a separate data frame that just has the coal combustion related rows

coalcomb <- scc[grepl("[Cc]oal", scc$EI.Sector), ]
coalscc <- coalcomb$SCC #99 different SCC values for coal combustion


#Each EI.Sector is connected to an SCC value
#I can get a list of the SCC values that are associated with each coal combustion
#I can then subset the dataframe to only include the scc values %in% that vector

rm(coal)

coal <- nei[nei$scc %in% coalscc, ] #Get only the rows that are associated with coal combustion

#Ok cool. I have a data frame that has just the rows I want

#Now I need to plot their emission data by year
coal$year <- factor(coal$year)

ggplot(coal, aes(x = year, y= emissions)) +
  stat_summary(fun = mean, geom = "bar", aes(fill = year)) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  xlab("Year") +
  ylab("Emissions from Coal Combustion") +
  labs(title = "Coal Combustion Emissions vs. Year") +
  theme_minimal()

```

